[Re] Chaos in a long-term experiment with a plankton community

### 2016-02-23 article/article.tex
latest build

The article stated: ``For short-term forecasts of only a few days, most
species had a high predictability of R2 = 0.70 -- 0.90 (Fig. 2).
However, the predictability of the species was much reduced when
prediction times were extended to 15--30days.'' The reproduced
predictabilities, which were calculated from the GAMs, were consistent
with these qualitative statements, though were quantitatively different
(\ref{fig:prediction_distance}). We did not reproduce the predictability
estimates for linear models.

@@

Considerable quantitative difference in predictability decay (figure
\ref{fig:prediction_distance}) remain unexplained, though could result
from original analyses using neural networks, and the reproduction using
GAMs.

>>>>

The article stated: ``For short-term forecasts of only a few days, most
species had a high predictability of R2 = 0.70 -- 0.90 (Fig. 2).
However, the predictability of the species was much reduced when
prediction times were extended to 15--30days.'' The reproduced
predictabilities, which were calculated from the GAMs, were consistent
with these qualitative statements, and were most often quantitatively
similar (\ref{fig:prediction_distance}). We did not reproduce the
predictability estimates for linear models.

@@

Quantitative differences in predictability decay (figure
\ref{fig:prediction_distance}) remain unexplained, though could result
from original analyses using neural networks, and the reproduction using
GAMs. The difference in estimate of the global Lyapunov exponent (0.08
in the original article and 0.04 here) appears to be due to difference
in data used (illustrated in figure \ref{fig:trans_comp2}).
